Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
graphs

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={noContext, noTypes, all},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{removing-features-2.csv};
\end{axis}
\end{tikzpicture}
\caption{Accuracy when features are removed, based on decision trees on a
random subset of 20000 program pairs.
\fixme{The x-axis labels are not perfectly clear: does ``all'' mean that
everything is still in or that everything is out?}
\fixme{Indicate that this is a top-1 model.}
\fixme{Normal the y-axis so that ``all'' is 1.0 to make the subset effects
more evident.}
}
\label{fig-removing-features}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={baseline, Type, Attribute, Value, Key, Index},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{defect-categories-2.csv};
\end{axis}
\end{tikzpicture}
\caption{Accuracy when the model is trained and tested on only the data exhibiting
the error on the x-axis.
\fixme{Spin this for generality. Indicate that our model gives high-quality
fault localization regardless of defect type. To put it another way, we
can view this as a sensitivity analysis: our algorithm is not sensitive to
defect type (that's good!).}
}
\label{fig:defect-categories}
\end{figure}

>>>>

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={No Context, No Types},
    xtick=data,
    ymin=0,
    ymax=1.1,
    ylabel=Normalized Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{removing-features-2-normalized.csv};
    \draw [red] ({rel axis cs:0,0}|-{axis cs:No Types,1}) -- ({rel axis cs:1,0}|-{axis cs:No Types,1}) node [pos=0.33, above] {};
\end{axis}
\end{tikzpicture}
\caption{Accuracy when features are removed, based on Top-1 decision trees on a
random subset of 20000 program pairs, as compared to a Top-1 decision tree trained
on all features.
}
\label{fig-removing-features}
\end{figure}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={Index, Value, Key, Type, Attribute},
    xtick=data,
    ymin=0,
    ylabel=Normalized Model Accuracy,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{defect-categories-2-normalized.csv};
    \draw [red] ({rel axis cs:0,0}|-{axis cs:Index,1}) -- ({rel axis cs:1,0}|-{axis cs:Index,1}) node [pos=0.33, above] {};
\end{axis}
% \begin{axis}
%     \addplot{1};
% \end{axis}
\end{tikzpicture}
\caption{Accuracy when a Top-1 decision tree is trained and tested on only the data exhibiting
the error on the x-axis, as compared to a Top-1 decision tree on all the data.
\fixme{Spin this for generality. Indicate that our model gives high-quality
fault localization regardless of defect type. To put it another way, we
can view this as a sensitivity analysis: our algorithm is not sensitive to
defect type (that's good!).}
}
\label{fig:defect-categories}
\end{figure}
